---
title: "Quantifying the Uncertainty of GHG extensions in MRIO"
format: html

---


## Description

This is the main script. 
It runs the individual R scripts in the required order. 

## Packages

```{r}
library(callr)
```


## Adjust config file


1. Adjust the paths to the data file (the directory where you saved the data downloaded as indicated above)
2. Adjust the number of cores to the characteristics of your computer (The more cores you use, (1) the faster the code runs, but also (2) the more RAM you require).

```{r}
file.edit('config.yml')
```

The version number determines where the intermediate results are stored. This means when you run the scripts the first time with a give version number a sub-folder under ./intermediate_results is created. Running the scripts again with the same version number overwrites the results.


## Execute Scripts

```{r} 
rscript("0_prepare_CT.R")
```

```{r} 
rscript("1a_create_CT_CRF_classification.R")
```

```{r} 
rscript("1b_prepare_UNFCCC_CRF.R")
```

```{r} 
rscript("1c_prepare_UNFCCC_uncertainty.R")
```

```{r} 
rscript("1d_repair_CRF_categories.R")
```

```{r} 
rscript("1e_merge_CRF_NIR_data.R")
```

```{r} 
rscript("1f_sample_UNFCCC.R")
```

```{r} 
rscript("2a_parse_EDGAR_emissions.R")
```

```{r} 
rscript("2b_parse_EDGAR_uncertainty.R")
```

```{r} 
rscript("2c_sample_EDGAR.R")
```

```{r} 
rscript("3a_prepare_SUT_proxies.R")
```

```{r} 
rscript("3b_prepare_PEFA_proxies.R")
```

```{r} 
rscript("3c_prepare_EMPLOYMENT_proxies.R")
```

```{r} 
rscript("3d_prepare_ROAD_TRANSPORT_proxies.R")
```

```{r} 
rscript("4a_residence_adjustment_SEA_prepare_data.R")
```

```{r} 
rscript("4b_residence_adjustment_SEA_sample.R")
```

```{r} 
rscript("4c_residence_adjustment_AIR_prepare.R")
```

```{r} 
rscript("4d_residence_adjustment_AIR_sample.R")
```

```{r} 
rscript("4e_residence_adjustment_ROAD_prepare.R")
```

```{r} 
rscript("5a_UNFCCC_get_EXIOBASE_proxies.R")
```

```{r} 
rscript("5b_EDGAR_get_proxies.R")
```

```{r} 
rscript("6a_combine_UNFCCC_EDGAR_samples.R")
```

```{r} 
rscript("6b_residence_adjustment_ROAD_sample.R")
```

```{r} 
rscript("6c_run_optimizer.R")
```

```{r} 
rscript("6d_sample_EXIOBASE.R")
```

```{r} 
rscript("6e_prepare_EXIOBASE_samples.R")
```

```{r} 
rscript("6f_convert_to_matrix.R")
```

```{r} 
rscript("7a_prepare_EXIOBASE.R")
```

```{r} 
rscript("7b_prepare_oecd_AEA.R")
```

```{r} 
rscript("8a_calculate_footprints.R")
```

```{r} 
rscript("8b_prepare_footprints.R")
```

```{r} 
rscript("9_plot_results.R")
```





